A general Nullstellensatz for generalised spaces

### 2019-07-10 slides-edinburgh2019.tex
Final version of the Edinburgh slides

  The photos on the slide are of \emph{Arthur's Seat}, a beautiful extinct
  volcano in Edinburgh. It gives an excellent view of the city and is very much
  recommended for a hiking tour.
  }%
\end{frame}}
\addtocounter{framenumber}{-1}

@@

  There is a notion of a \emph{model} of a geometric theory in
  any given topos. For instance, a ring in the usual sense is a model of the
  theory of rings in the topos~$\Set$. The structure sheaf of a scheme~$X$ is a
  model in the topos~$\Sh(X)$ of set-valued sheaves on~$X$.

@@

      \begin{column}{0.45\textwidth}
        \includegraphics[width=\textwidth,align=t]{mike-shulman-stack-semantics}
        \vspace*{1.5em}
      \end{column}
    \end{columns}
  }

@@

  This observation unlocks a short and conceptual proof of Grothendieck's
  generic freeness lemma.

>>>>

  The photos on the slide are of \emph{Arthur's Seat}, a beautiful extinct
  volcano in Edinburgh where parts of these slides have been created. It gives
  an excellent view of the city and is very much recommended for a hiking tour.
  }%
\end{frame}}
\addtocounter{framenumber}{-1}

@@

  There is a notion of a \emph{model} of a geometric theory in
  any given topos. For instance, a ring in the usual sense is a model of the
  theory of rings in the topos~$\Set$. The structure sheaf~$\O_X$ of a scheme~$X$ is a
  model in the topos~$\Sh(X)$ of set-valued sheaves over~$X$.

@@

      \begin{column}{0.45\textwidth}
        \href{https://arxiv.org/abs/1004.3802}{\includegraphics[width=\textwidth,align=t]{mike-shulman-stack-semantics}}
        \vspace*{1.5em}
      \end{column}
    \end{columns}
  }

@@

  This observation unlocks a short and conceptual proof of Grothendieck's
  generic freeness lemma in algebraic geometry.
